\TitlePt

### 2016-03-28 paper-tesseroids.tex
Add new section with links to online material
suggested by Val

This chapter has been submitted for publication in the journal Geophysics in
collaboration with Dr. Carla Braitenberg of the University of Trieste, Italy.

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online\footnote{
http://tesseroids.leouieda.com}\footnote{
http://dx.doi.org/10.5281/zenodo.16033}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in an online repository\footnote{
https://github.com/pinga-lab/paper-tesseroids}.

@@

>>>>

This chapter has been submitted for publication in the ``Geophysical Software
and Algorithms'' section of the journal GEOPHYSICS.

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in version 1.2 of the open-source package \emph{Tesseroids}.
It is freely available online\footnote{
\url{http://tesseroids.leouieda.com}}\footnote{
\url{http://dx.doi.org/10.5281/zenodo.16033}}
under the BSD 3-clause open-source license.
An archived version of the source code
is also available as part of this article.

@@

The IPython notebooks
and the data generated for the error analysis,
as well as instructions for installing the software
and running the programs,
are also included in
the source code archive that accompanies this article.
Alternatively,
all accompanying material is available
in an online repository\footnote{
\url{https://github.com/pinga-lab/paper-tesseroids}}.

@@

\section{Online repository}

The source code, compiled binary files, and user documentation for
\textit{Tesseroids} can be found at the project website
\url{http://tesseroids.leouieda.com}.
The source code for version 1.2 of \textit{Tesseroids} is permanently archived
at \url{http://dx.doi.org/10.5281/zenodo.16033}.
The data and source code that produced the results and figures presented here
can be downloaded from
\url{https://github.com/pinga-lab/paper-tesseroids}.
